Blueprint for efficient nuclear spin characterization with color center

### 2024-05-07 PRB - revision reply/main_revision.tex
revision

Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$.

>>>>

Where $\vec{n}_0 \cdot \vec{n}_1 = \frac{\omega_L^2+(s_0+s_1)A_{zz}+s_0 s_1 (A_{zz}^2+A_{zx}^2)}{\omega_0 \omega_1}$, \textcolor{blue}{which is the inner product of precession axes of a nuclear spin condition on the electron spin sublevel. This expression indicates the advantage of using DD sequence for sublevels where either $s_0$ or $s_1$ is zero, only first order parallel hyperfine coupling $\frac{A_{zz}}{\omega_L}$ play a role. On the other hand, in spin-1/2 systems ($s_0=-\frac{1}{2}$ and $s_1=\frac{1}{2}$), the first order hyperfine coupling vanishes and only second order parallel hyperfine coupling $(\frac{A_{zz}}{\omega_L})^2$ and second order perpendicular hyperfine coupling $(\frac{A_{zx}}{\omega_L})^2$ remain present. This indicates weak sensitivity of DD sequence on different nuclear spins.}
